Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-30 paper.qmd
Fix the issue not appearing space after p-D and k-D
Changed font size of the notation table

bibliography: bibliography.bib  
header-includes: | 
  \usepackage{amsmath}
  \usepackage{float}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \newcommand\pD{$p\text{-}D$}
  \newcommand\kD{$k\text{-}D$}
---

@@

# Create the table
kable(notation_df, format = "latex", booktabs = TRUE, escape = FALSE, 
      caption = "Notations used in this paper.", label = "tbl-notations") |>
  kable_styling(full_width = FALSE) |>
  row_spec(0, bold = TRUE)
```

>>>>

bibliography: bibliography.bib  
header-includes: | 
  \usepackage{amsmath}
  \usepackage{float}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{setspace}
  \newcommand\pD{$p\text{-}D$\ }
  \newcommand\kD{$k\text{-}D$\ }
---

@@

# Create the table
kable(notation_df, format = "latex", booktabs = TRUE, escape = FALSE, 
      caption = "Notations used in this paper.", label = "tbl-notations") |>
  kable_styling(latex_options = c("HOLD_position"), position = "center", full_width = FALSE, font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("5cm", "12cm"))
```
